Russian sanctions figures

### 2024-04-19 ms-russia-figures.Rmd
Add stats for MS text

>>>>

# Percent of US consumption moving through intermediate country
consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>% 
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "direct", 
    TRUE ~ "indirect"
  )) %>%
  group_by(path) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(percent = 100*consumption_live_t/sum(consumption_live_t))
